```{r setup, include=FALSE}
options(warn=-1)
if (!require("pacman")) install.packages("pacman")
pacman::p_load("renv", "here", "knitr")

knitr::opts_chunk$set(echo = TRUE)

here::i_am(".losartan_hidden_root")
here::here()

# renv::init()
renv::activate(here::here(""))
#renv::restore(project=here::here(""))
#renv::snapshot()
dir.create(here::here("output/figures/"))

data_dir = here::here('data')
utils_dir = here::here('utils' )

adjustment_method ="holm"
```

## Load packages
```{r}
#library(devtools)
#devtools::install_github("mattelisi/mlisi") 
#devtools::install_github("mattelisi/bmsR")

required_packages = c("reshape2", "sjmisc", "sjPlot", "purrr", "ggpubr", "corrplot", "dplyr","ggplot2", "ggsignif", "parameters", "extdplyr", "Jmisc", "PupillometryR",  "plyr", "lme4", "lmerTest", "emmeans", "tidyr", "ggpubr", "corrplot", "patchwork", "broom", "plotrix", "PupillometryR","glmmTMB", "Hmisc", "boot", "data.table", "devtools", "bmsR", "performance", "extdplyr")
pacman::p_load(char = required_packages) 

library(emmeans)


source(here::here(utils_dir, 'r_functions.R'))
pal <- get_colors("ond")
emm_options(pbkrtest.limit = 5000)

run_descriptives <- function(df, vec) {
  sdf <- df[, append("drug_str", vec)]
  for (i in as.character(vec)) {
    tsdf = sdf %>%
      group_by(drug_str) %>%
      summarise_at(i, funs(mean,sd),na.rm = TRUE)
    tsdf$varname <- i
    print(tsdf)
  }
  pvals <- sdf %>%
        summarise_each(funs(t.test(.[drug_str == "losartan"], .[drug_str == "placebo"])$p.value), vars =  vec)
  tscores <- sdf %>%
        summarise_each(funs(t.test(.[drug_str == "losartan"], .[drug_str == "placebo"])$statistic), vars =  vec)
  dfs <- sdf %>%
        summarise_each(funs(t.test(.[drug_str == "losartan"], .[drug_str == "placebo"])$parameter), vars =  vec)
  
  stats <- rbind(pvals, tscores, dfs, vec)
  stats <- data.table::transpose(stats)
  colnames(stats) <- c("p", "t", "df", "variable")
  
  print(stats)
}
```

# 1/ Descriptive and control analyses
```{r}
#prepare data for this entire section
data<-read.csv(here::here(data_dir, "data_across_mods_pupiltype_amplitude.csv"))
df<-data[which(data$visit_str %in% c("v2")),]
#check! df[,c("group_raw", "drug_str")] gooD!
df$sb <- paste0("sp", as.factor(df$sb_mdata))

df$lang <- as.character(df$X1stlang)
df$lang[!(df$lang %in% "engl")] <- "other"
```

```{r}
vec <- c("heart_rate_base",   "heart_rate_peak")
run_descriptives(df, vec)
```
## 1a/ Sociodemographic data (Table 1)
- gender
- first language english
- age
- NART
- years of education

```{r}

#df$education <- as.numeric(df$education)
sdf <- df[, c("drug_str", "Gender", "NART", "Age", "education", "lang" )]

## Means
for (i in as.character(c( "NART", "Age", "education"))) {
  tsdf = sdf %>%
    group_by(drug_str) %>%
    summarise_at(i, funs(mean,sd),na.rm = TRUE)
  print(tsdf)
}

# Frequencies/percentages
tsdf = sdf %>%
  group_by( drug_str, Gender) %>%
  pct_routine(ret_name = "pct")
print(tsdf)

  tsdf = sdf %>%
  group_by( drug_str, lang) %>%
  pct_routine(ret_name = "pct")
print(tsdf)
  
vec <- c("NART", "Age", "education")
# T-tests on continuous variables
pvals <- sdf %>%
        summarise_each(funs(t.test(.[drug_str == "losartan"], .[drug_str == "placebo"])$p.value), vars = vec)
tscores <- sdf %>%
        summarise_each(funs(t.test(.[drug_str == "losartan"], .[drug_str == "placebo"])$statistic), vars =  vec)
dfs <- sdf %>%
      summarise_each(funs(t.test(.[drug_str == "losartan"], .[drug_str == "placebo"])$parameter), vars =  vec)

stats <- rbind(pvals, tscores, dfs, vec)
stats <- data.table::transpose(stats)
colnames(stats) <- c("p", "t", "df", "variable")

print(stats)


# Chi-squared test on freq
sdf$drug_str <- as.character(sdf$drug_str)
sdf$Gender <- as.character(sdf$Gender)
sdf$lang <- as.character(sdf$lang)

chisq <- chisq.test(table(sdf$drug_str, sdf$Gender))
chisq

chisq <- chisq.test(table(sdf$drug_str, sdf$lang))
chisq

```

## 1b/ Clinical and Personality Measures (Table 1)
- STAI-TAIT  
- ASI
- BDI 
- EPQ (neuroticism)
- Attentional control (ACS), subdivision to total, focusing and shifting

```{r}
vec <- c(  "STAIT",   "ASI",  "BDI",   "EPQ_N",  "ACS_total", "ACS_Focussing", "ACS_Shifting")
run_descriptives(df, vec)

```


## 1c/ Drug effect on physiological and VAS measures (Table 2)
(all before and at peak)
- HR 
- blood pressure sys
- blood pressure dia 
VAS scale:
- anxious
- tearful
- hopeless
- sad
- depressed
- sleepy 
- nauseous
- dizzy
- heart racing 
- alert

```{r}

## Heart rate
vec <- c("heart_rate_base",   "heart_rate_peak")
run_descriptives(df, vec)
df$vas_T1_hr <- df$heart_rate_base
df$vas_T2_hr <- df$heart_rate_peak


## Blood pressure
vec <- c("blood_pressure_base_syst",  "blood_pressure_base_diast", "blood_pressure2_syst", "blood_pressure2_diast")
run_descriptives(df, vec)
df$vas_T1_bpsys <- df$blood_pressure_base_syst 
df$vas_T2_bpsys <- df$blood_pressure2_syst
df$vas_T1_bpdia <- df$blood_pressure_base_diast
df$vas_T2_bpdia <- df$blood_pressure2_diast


## VAS measures
vars<- c("anx", "tearful", "hopeless", "sad", "depr", "sleep", "nauseous","dizzy", "tachy", "alert", "flushed")
for (t in  c("vas_T1_", "vas_T2_", "vas_T3_")) {
  vec <- paste(t, vars, sep="")
  sdf <- df[, append("drug_str", vec)]
  for (i in as.character(paste(t, vars, sep=""))) {
    tsdf = sdf %>%
      group_by(drug_str) %>%
      summarise_at(i, funs(mean,sd),na.rm = TRUE)
    tsdf$varname <- i
    print(tsdf)
  }
pvals <- sdf %>%
      summarise_each(funs(t.test(.[drug_str == "losartan"], .[drug_str == "placebo"])$p.value), vars =  vec)
tscores <- sdf %>%
        summarise_each(funs(t.test(.[drug_str == "losartan"], .[drug_str == "placebo"])$statistic), vars =  vec)
dfs <- sdf %>%
      summarise_each(funs(t.test(.[drug_str == "losartan"], .[drug_str == "placebo"])$parameter), vars =  vec)

stats <- rbind(pvals, tscores, dfs, vec)
stats <- data.table::transpose(stats)
colnames(stats) <- c("p", "t", "df", "variable")
print(stats)

}

vars <- append(c("hr", "bpsys", "bpdia"), vars )
### VAS measures F-tests!
for (v in vars) {
  vec <- paste(c("vas_T1_", "vas_T2_"), v, sep="")
  ldf <- df[, append("drug_str", vec)]
  ldf<-tidyr::pivot_longer(data=ldf, cols=vec, names_to="visit", values_to=v)
  m<-lm(data=ldf, paste0(v, " ~ drug_str*visit"))
  an <- anova(m)
  print(an)
}


```

### change in blood pressure before/after administration
```{r}
#df$vas_T1_bpsys <- df$blood_pressure_base_syst 
#df$vas_T2_bpsys <- df$blood_pressure2_syst
#df$vas_T1_bpdia <- df$blood_pressure_base_diast
#df$vas_T2_bpdia <- df$blood_pressure2_diast
df$id <- df$ids_Q

phys_df = df

df_sys <- df %>% 
     reshape2::melt(id.vars = c("id", "drug_str"),  # variables to carry forward
          measure.vars = c("vas_T1_bpsys", "vas_T2_bpsys"),  #variables to stack
          value.name = "bpsys",     # name of the value variable 
          variable.name = "time" ) # name of the variable    


df_dia <- df %>% 
     reshape2::melt(id.vars = c("id", "drug_str"),  # variables to carry forward
          measure.vars = c("vas_T1_bpdia", "vas_T2_bpdia"),  #variables to stack
          value.name = "bpdia",     # name of the value variable 
          variable.name = "time" ) # name of the variable  

df_sys2 <- df_sys %>%
  group_by(time,drug_str) %>%
  summarise_at(c("bpsys"), mean, na.rm = TRUE)
df_sys2

df_dia2 <- df_dia %>%
  group_by(time, drug_str) %>%
  summarise_at(c("bpdia"), mean, na.rm = TRUE)
df_dia2



m<- lm(data=df_sys, bpsys~time*drug_str)
anova(m)

m<- lm(data=df_dia, bpdia~time*drug_str)
anova(m)



```


## 1d/ Data quality 
shock magnitude (calibration)
starting probability 
difference between safe and harmful cue (present as control, only 20% of trials each) 

```{r}
## Task properties
vec <- c(  "sh_int", "first_prob")
run_descriptives(df, vec)

sdf <- df[, c("drug_str", "sb")]
sdf$sb <- as.character(sdf$sb)
sdf <- sdf[sdf$drug_str %in% c("losartan", "placebo"),]
chisq <- chisq.test(table(sdf$drug_str, sdf$sb)[c("losartan", "placebo"), c("sp25", "sp75")])
#chisq <- chisq.test(sdf)
chisq
table(sdf$drug_str, sdf$sb)[c("losartan", "placebo"), c("sp25", "sp75")]/20

```
## /1e

```{r}
data<-read.csv(here::here(data_dir, "data_across_mods_pupiltype_amplitude.csv"))
df<-data[which(data$visit_str %in% c("v2")),]

table(df$demand_exp, df$drug_str)[c("losartan", "placebo"), c("losartan", "placebo")]
16/40

table(df$demand_pat, df$drug_str)[c("losartan", "placebo"), c("losartan", "placebo")]
20/40

chisq.test(table(df$demand_exp, df$drug_str)[c("losartan", "placebo"), c("losartan", "placebo")])
chisq.test(table(df$demand_pat, df$drug_str)[c("losartan", "placebo"), c("losartan", "placebo")])


```


# 2/ Behavioural analyses
## 2a-1/ Estmated switchpoint (for realigning the data)
```{r}
data<-read.csv(here::here(data_dir, "p3_est_switch_data.csv"))
data<- data[data$visit %in% c(1,2, 3),]
data["drug_str"] =  data["group"]
data<-data[which(data$phase_str %in% c("acq","ext")),]
fields <- c("visit", "phase_str", "drug_str", "outcome", "id", "sb")
data2<- assign_var_types(data, fields)

df = data2 %>%
  group_by(id, drug_str, visit_str, sb, phase_str) %>%
  summarise_at("switchpoint", mean, na.rm = TRUE)
pal <- get_colors("ond")
g <- ggplot(data = df, aes(y = switchpoint, x = visit_str, fill = drug_str)) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8, show.legend = FALSE, lwd=1.2) +
geom_point(aes(y = switchpoint, colour=drug_str), position = position_jitter(width = .15), size = 1, alpha = 0.8, show.legend = FALSE) +
geom_boxplot(width = .2, outlier.shape = NA, alpha = 0.7,lwd=1.2, show.legend = TRUE) +
#geom_label(data = df2, aes(label = BIC, x = model, fill = drug_str, y = 100),  size=5) +
expand_limits(x = 3) +
scale_color_manual(values = c(pal[8], pal[10]), name = "group", labels = c("placebo", "losartan")) +
scale_fill_manual(values = c(pal[8], pal[10]), name = "group", labels = c("placebo", "losartan")) +  
theme_bw() +
raincloud_theme 

g

m <- lmer(switchpoint ~ drug_str*visit_str*phase_str + (1|id)  + (1|sb) , data2) # without half
anova(m)
joint_tests(m, by = c("visit_str"))
em <- emmeans(m, specs = pairwise ~ visit_str*drug_str, adjust=adjustment_method)
em$emmeans
em$contrasts

mean(data2$switchpoint)
sd(data2$switchpoint)

```

## 2a-3 Stable cues
The difference on visit o
```{r}
data<-read.csv(here::here(data_dir,  "full_beh_dataset_p3.csv"))
data<-data[which(data$Trial_Type %in% c(1,2) & (data$visit %in% c(2))),]# & (data$Reversal_ID %in% c(1,2,3,4,5,6))),]
fields <- c("visit", "trtype_str", "drug", "outcome", "id")
data$err <- data$err_true
data<- assign_var_types(data, fields)
df <- data %>%
  group_by(id, drug_str,  trtype_str, sb) %>%
  summarise_at(c("err", "prob"), mean, na.rm = TRUE)
#emm_options(pbkrtest.limit = 7380)
m <- lmer(prob ~   drug_str*trtype_str + (1|id) + (1|sb), data=df)
anova(m)
emmeans(m, pairwise ~ drug_str*trtype_str, adjust=adjustment_method)

t.test(data=df[df$trtype_str %in% "low-prob",], prob ~ drug_str )
t.test(data=df[df$trtype_str %in% "hi-prob",], prob ~ drug_str )

# one-way t-tests against true reinforcement rates
df2 <- df %>% 
    group_by(drug_str,trtype_str) %>%
    nest() %>% 
    dplyr::mutate(tt=purrr::map(data,~t.test(.x$err))) %>%
    dplyr::mutate(tidied = purrr::map(tt, tidy)) %>% 
    unnest(tidied, .drop = T)



df2$p.value.holm= p.adjust(df2$p.value, method = adjustment_method)
df2$sig <- 0 
df2$sig[df2$p.value.holm<0.05] <- 1
print(df2[,c("drug_str", "trtype_str", "estimate",     "statistic", "parameter", "p.value.holm")])

```


## 2b/ Realigned behavioural data
### 2b-1/ reversal-locked plot

```{r fig.width=10, fig.height=4}
data<-read.csv(here::here(data_dir,  "full_beh_dataset_p3.csv"))
data<-data[which(data$Trial_Type %in% 3),]
data<-data[which(data$trno_swchp %in% c(seq(-5, -1), seq(1,15))),]
data<-data[which(data$rev_type_4plot_swchp %in% c("acq","ext")),]
fields <- c("visit", "rev_type_4plot_swchp", "drug", "outcome", "id")
df<- assign_var_types(data, fields)

## This step is important for PLOTTING - it weights participants equally
df = df %>%
  group_by(trno_swchp, id, drug_str, visit_str, rev_type_4plot_swchp) %>%
  summarise_at("prob", mean, na.rm = TRUE)

df = df %>%
  group_by(trno_swchp, drug_str, visit_str, rev_type_4plot_swchp) %>%
  summarise_at("prob", funs(mean,std.error),na.rm = TRUE)
df$lower = df$mean - df$std.error
df$upper = df$mean + df$std.error

pal <- get_colors("ond")
g <- ggplot(data = df, aes(y = mean, x = trno_swchp, fill=interaction(rev_type_4plot_swchp, drug_str))) +
  geom_vline(xintercept=0, linetype="dashed") +
  geom_line(size=1.5, show.legend = TRUE) +
  geom_ribbon(aes(ymin=lower, ymax=upper),  na.rm = TRUE,alpha=0.6,show.legend = TRUE) + 
  scale_fill_manual(values = c(pal[2], pal[4], pal[1], pal[3]), name = "", labels = c("High Threat: Losartan", "Low Threat: Losartan", "High Threat: Placebo", "Low Threat: Placebo")) +
   scale_color_manual(values = c(pal[2], pal[4], pal[1], pal[3])) + 
  ylim(0,1) + 
  scale_x_continuous(breaks = c(-5, -1, 1, 5, 10), limits=c(-5,10)) +
  theme_bw() +
  labs(y= "Rating", x="Trial (locked to estimated switchpoint)")  +
  ggtitle("Participant data") + 
  raincloud_theme   +
  facet_grid(cols=vars(visit_str))
g

erdf <- df

ggsave(here::here(figures_dir, "Fig2", "Figure2_raw.pdf"), width = 10, height = 5, dpi = 120)

```


### 2b-2/ Adjustment of probabilities (trials 5-15 after switch, baselin subtracted)

```{r}

data<-read.csv(here::here(data_dir,  "full_beh_dataset_p3.csv"))

data<-data[which(data$Trial_Type %in% 3),]
data<-data[which(data$trno_swchp %in% c(seq(-5, -1), seq(5,15))),]
data<-data[which(data$rev_type_4plot_swchp %in% c("acq","ext")),]
data <- data %>% mutate(prepost = 
                    case_when(trno_swchp %in% seq(-3,-1) ~ "pre", 
                              trno_swchp %in% seq(5, 15) ~ "post"), na.rm = TRUE)
data<-data[which(data$prepost %in% c("pre","post")),]
fields <- c("visit", "rev_type_4plot_swchp", "drug", "outcome", "id", "prepost", "sb")
data<- assign_var_types(data, fields)

### Get baseline for each reversal 
dfbase <- data[data$prepost %in% "pre", c("prob", "prepost", "id", "rev_id_swchp", "drug_str", "visit_str", "rev_type_4plot_swchp", "sb")]
dfbase = dfbase %>%
  group_by(id, rev_id_swchp, drug_str, visit_str, rev_type_4plot_swchp, sb) %>%
  summarise_at("prob", mean, na.rm = TRUE)
dfbase$prob_baseline <- dfbase$prob
dfbase <- dfbase[,c("id", "visit_str", "rev_id_swchp", "prob_baseline")]

### Get summarized data and append base
df <- data[, c("prob", "prepost", "id", "rev_id_swchp", "drug_str", "visit_str", "trno_swchp", "rev_type_4plot_swchp", "sb")]
df = df[data$prepost %in% "post",]
df <- base::merge(df, dfbase, by=c("id", "visit_str", "rev_id_swchp"))

### Subtract baseline
df$probchange <- df$prob - df$prob_baseline



## Add approx true prob
i <- 1
lvls <- c(0.75, 0.25)
for (ph in c("acq", "ext" )) {
  df$truechange[df$rev_type_4plot_swchp %in% ph] <- lvls[i] - df$prob_baseline[df$rev_type_4plot_swchp %in% ph]
  i <- i + 1
}

##### STATS ########################################################################

m <- lmer(data=df, probchange ~ drug_str*visit_str*rev_type_4plot_swchp + (1|sb) + (1|id))
anova(m)
effectsize::effectsize(anova(m), type="eta", alternative="two.sided")

df$model_pred <- predict(m) # for plotting

## POST-HOCS
#main eff phase
em2<-emmeans(m, pairwise ~ rev_type_4plot_swchp, adjust=adjustment_method)
em2

em <- emmeans(m, ~ visit_str | drug_str/rev_type_4plot_swchp, adjust=adjustment_method)
em
pairs(em, adjust=adjustment_method)
pairs(pairs(emmeans::regrid(em)), by = NULL)  

# differnces on each visit 
em <- emmeans(m, ~ drug_str | rev_type_4plot_swchp /visit_str) 
pairs(em, adjust=adjustment_method)
pairs(pairs(emmeans::regrid(em)), by = NULL)  

#contrast of contrasts: is the (los-plac) difference between acq and ext significant?
# (losartan - placebo acq v1) - (losartan - placebo ext v1)  -0.0444 0.0303  6.05  -1.465  0.6953
# (losartan - placebo acq v2) - (losartan - placebo ext v2)  -0.1624 0.0208  3.02  -7.820  0.0202
# (losartan - placebo acq v3) - (losartan - placebo ext v3)  -0.2080 0.0308  4.45  -6.746  0.0107

#em <-  emmeans(m, pairwise ~ drug_str *rev_type_4plot_swchp * visit_str, adjust=adjustment_method)


em <- emmeans(m, specs = ~ drug_str * visit_str * rev_type_4plot_swchp)
em
### add to paper
lincombs <- contrast(em,
               list(v2_v1_drug_acq=c(-1,0,1,0,0,0,0,0,0,0,0,0),
                    v2_v1_drug_ext=c(0,0,0,0,0,0,-1,0,1,0,0,0),
                    v2_v1_plac_acq=c(0,-1,0,1,0,0,0,0,0,0,0,0),
                    v2_v1_plac_ext=c(0,0,0,0,0,0,0,-1,0,1,0,0),
                    
                    v3_v1_drug_acq=c(-1,0,0,0,1,0,0,0,0,0,0,0),
                    v3_v1_drug_ext=c(0,0,0,0,0,0,-1,0,0,0,1,0),
                    v3_v1_plac_acq=c(0,-1,0,0,0,1,0,0,0,0,0,0),
                    v3_v1_plac_ext=c(0,0,0,0,0,0,0,-1,0,0,0,1)
                    ), adjust=adjustment_method) # second one not changed
concon <- contrast(lincombs, list(acq_drug_plac_v2v1=c(1,0,-1,0,0,0,0,0),
                                  ext_drug_plac_v2v1=c(0,1,0,-1,0,0,0,0),
                                  acq_drug_plac_v3v1=c(0,0,0,0,1,0,-1,0),
                                  ext_drug_plac_v3v1=c(0,0,0,0,0,1,0,-1)), adjust=adjustment_method)
print(summary(concon))

```

### Plot mean adjustment 

```{r}

## PLOT ################################
dtrue = df %>%
  group_by(rev_type_4plot_swchp) %>%
  summarise_at("truechange", mean, na.rm = TRUE)

dft = df %>%
  group_by(id, drug_str, visit_str, rev_type_4plot_swchp, sb) %>%
  summarise_at(c("probchange", "model_pred"), mean, na.rm = TRUE)

dft$visit_str <- mapvalues(dft$visit_str,
                            from = c("v1", "v2", "v3"),
                            to =c("Baseline Session", "Drug Session", "Follow-up Session"))


g <- ggplot(data = dft, aes(y = probchange, x = rev_type_4plot_swchp, fill=interaction(rev_type_4plot_swchp, drug_str))) +
geom_hline(yintercept=c(0), linetype="dashed") +
geom_point(aes(color= interaction(rev_type_4plot_swchp, drug_str)), position =   position_jitterdodge(  jitter.width = .15,  dodge.width = 0.5), size = 2, alpha = 0.5, show.legend=FALSE) + 
geom_boxplot(inherit.aes = TRUE, width = .8, lwd=1.2, outlier.shape = NA, alpha = 1, show.legend=FALSE) + 
  stat_summary(geom="point", fun="mean", size=4, shape=23, aes(y=model_pred, group=interaction(rev_type_4plot_swchp, drug_str)), color="black", 
             position = position_dodge( 0.8), stroke=1.5, show.legend = FALSE) +
  scale_fill_manual(values = c(pal[1], pal[2], pal[3], pal[4])) +
   scale_color_manual(values = c(pal[1], pal[2], pal[3], pal[4])) + 
expand_limits(x = 3) +
theme_bw() +
raincloud_theme +
theme(legend.position = "right",
      strip.text.x = element_text(size = 12,  face = "bold"),
      strip.background = element_rect(color="black", fill="#ebebeb", size=0, linetype="solid")
      ) + 
labs(y= "Baseline-corrected probability ratings", x="Threat phase")  +
scale_x_discrete(labels=c("acq" = "high", "ext" =  "low")) + 
scale_y_continuous(breaks = c(-0.5,0,0.5)) +
  
facet_grid(cols=vars(visit_str)) 
g
ggsave(here::here(figures_dir, "Fig2", "Figure2b_raw.pdf"), width = 10, height = 5, dpi = 120)



```

#### Change low-to-high > high-to-low

```{r}
data<-read.csv(here::here(data_dir,  "full_beh_dataset_p3.csv"))

data<-data[which(data$Trial_Type %in% 3),]
data<-data[which(data$trno_swchp %in% c(seq(-5, -1), seq(5,15))),]
data<-data[which(data$rev_type_4plot_swchp %in% c("acq","ext")),]
data <- data %>% mutate(prepost = 
                    case_when(trno_swchp %in% seq(-3,-1) ~ "pre", 
                              trno_swchp %in% seq(5, 15) ~ "post"), na.rm = TRUE)
data<-data[which(data$prepost %in% c("pre","post")),]
fields <- c("visit", "rev_type_4plot_swchp", "drug", "outcome", "id", "prepost", "sb")
data<- assign_var_types(data, fields)

### Get baseline for each reversal 
dfbase <- data[data$prepost %in% "pre", c("prob", "prepost", "id", "rev_id_swchp", "drug_str", "visit_str", "rev_type_4plot_swchp", "sb")]
dfbase = dfbase %>%
  group_by(id, rev_id_swchp, drug_str, visit_str, rev_type_4plot_swchp, sb) %>%
  summarise_at("prob", mean, na.rm = TRUE)
dfbase$prob_baseline <- dfbase$prob
dfbase <- dfbase[,c("id", "visit_str", "rev_id_swchp", "prob_baseline")]

### Get summarized data and append base
df <- data[, c("prob", "prepost", "id", "rev_id_swchp", "drug_str", "visit_str", "trno_swchp", "rev_type_4plot_swchp", "sb")]
df = df[data$prepost %in% "post",]
df <- base::merge(df, dfbase, by=c("id", "visit_str", "rev_id_swchp"))

### Subtract baseline
# 
df$probchange <- df$prob - df$prob_baseline
# flip extinction for direct compariosn of acq and ext
df$probchange[df$rev_type_4plot_swchp %in% "ext"] <- df$probchange[df$rev_type_4plot_swchp %in% "ext"] * (-1)

m <- lmer(data=df, probchange ~ drug_str*visit_str*rev_type_4plot_swchp + (1|sb) + (1|rev_id_swchp/id))

em <- emmeans(m, specs = ~ drug_str * visit_str * rev_type_4plot_swchp)
em
lincombs <- contrast(em,
               list(v2_v1_drug_acq=c(-1,0,1,0,0,0,0,0,0,0,0,0),
                    v2_v1_drug_ext=c(0,0,0,0,0,0,-1,0,1,0,0,0),
                    v3_v1_drug_acq=c(-1,0,0,0,1,0,0,0,0,0,0,0),
                    v3_v1_drug_ext=c(0,0,0,0,0,0,-1,0,0,0,1,0)), 
               adjust=adjustment_method) # second one not changed
concon <- contrast(lincombs, list(acq_ext_drug_v2=c(-1,1,0,0),
                                  acq_ext_drug_v3=c(0,0,-1,1)), adjust=adjustment_method)
print(summary(concon))
```

### 2b-3/ error from true rates in reversal cue 
```{r fig.width=10, fig.height=4}

data<-read.csv(here::here(data_dir,  "full_beh_dataset_p3.csv"))

data<-data[which(data$Trial_Type %in% 3),]
data<-data[which(data$trno_swchp %in% c(seq(5,15))),]
data<-data[which(data$rev_type_4plot_swchp %in% c("acq","ext")),]
data<-data[(data$visit %in% c(1,2,3)),]# & (data$Reversal_ID %in% c(1,2,3,4,5,6))),]
fields <- c("visit", "rev_type_4plot_swchp", "drug", "outcome", "id")
data$err <- data$err_true
data<- assign_var_types(data, fields)
df <- data %>%
  group_by(id, sb, drug_str, visit_str, rev_type_4plot_swchp) %>%
  summarise_at(c("err", "prob"), mean, na.rm = TRUE)
errdata <- df

# one-way t-tests against true reinforcement rates
df2 <- df %>% 
    group_by(visit_str,drug_str, rev_type_4plot_swchp) %>%
    nest() %>% 
    dplyr::mutate(tt=purrr::map(data,~t.test(.x$err))) %>%
    dplyr::mutate(tidied = purrr::map(tt, tidy)) %>% 
    unnest(tidied, .drop = T)



df2$p.value.holm= p.adjust(df2$p.value, method = adjustment_method)
df2$p.value.holm <- round(df2$p.value.holm,3)
df2$p.value <- round(df2$p.value,3)
df2$sig <- 0 
df2$sig[df2$p.value.holm<0.05] <- 1
df3 <- df2[,c("drug_str", "visit_str",  "rev_type_4plot_swchp", "estimate",  "statistic", "parameter", "p.value", "p.value.holm")]
print(df3)

g<-ggplot(data=df3, aes(x=visit_str, y=statistic, color=interaction(visit_str, drug_str))) + 
  geom_point() + 
  geom_text(
    mapping = aes(label = paste0("p=", p.value.holm)), 
    nudge_x = -0.3
  ) + 
  facet_grid(cols=vars(rev_type_4plot_swchp))
g

```


# 3/ Modelling analyses 
## 3a/ Model comparison 
```{r fig.width=10, fig.height=4}

# load and filter data
data<-read.csv(here::here(data_dir, "p3_model_data_from_phase_1_to_end_full.csv"))
data<-data[which(data$cue %in% c("reversal")),]
fields <- c("visit", "drug_str", "cue", "model_str", "drug", "ids", "ta", "sb")
df<- assign_var_types(data, fields)
df$model_str <- mapvalues(df$model_str,
                            from = c("PHnk5", "RW3", "RW3ph", "RW5ph"),
                            #to =c("PH-5", "RW-outcome-3", "RW-phase-3", "RW-both-5"))
                            to =c("Pearce-Hall model", "Outcome-sensitive model", "Phase-sensitive model", "Phase- and outcome-sensitive model"))
pal <- get_colors("ond")


# PRINT BICs before demeaning
dftemp = df %>%
  group_by(model_str ) %>%
  summarise_at("BIC", mean, na.rm = TRUE)
print(dftemp)


dftemp = df %>%
  group_by(ids, model_str, drug_str ) %>%
  summarise_at("BIC", mean, na.rm = TRUE)

m<-lmer(data=dftemp, BIC ~ model_str*drug_str + (1|ids))
anova(m)



# reduce data
df = df %>%
  group_by(ids, model_str, drug_str, visit_str_nicer ) %>%
  summarise_at("BIC", mean, na.rm = TRUE)

# for demeaning, mean by visit
dem_df = df %>%
  group_by(visit_str_nicer, drug_str) %>%
  summarise_at(c("BIC"), mean, na.rm = TRUE)
dem_df$BICmean <- dem_df$BIC
dem_df$BIC <- NaN
df<- merge(x = df, y = dem_df, by = c("visit_str_nicer", "drug_str"), all.x = TRUE)
df$BIC_demean <- df$BIC.x - df$BICmean


# load and filter data
df_summ1 = df %>%
  group_by( model_str) %>%
  summarise_each(funs(mean,sd,se=sd(.)/sqrt(n())), BIC_demean)
print(df_summ1)
# Plot2
g <- ggplot(df_summ1, aes(x=model_str, y=mean, fill=model_str)) + 
          geom_bar(inherit.aes = TRUE, stat = "summary", fun.y = "mean", color="black", show.legend = TRUE, width=0.8, lwd=1) + 
          scale_fill_manual(values = pal[c(15,16,17,18)], name = "Model") +
          labs(y= "BIC (demeaned)", x="Model")  +
          theme_bw() +
          raincloud_theme  +
          theme(axis.text.x=element_text(angle = -90, hjust = 0, vjust = 0.35)) + 
          scale_x_discrete(label=c("","","", ""))
g
ggsave(here::here(figures_dir, "Fig3", "Figure3b_raw.pdf"), width = 7, height = 3, dpi = 120)

```

### Percentage of people best fitted by each model 
```{r}
data<-read.csv(here::here(data_dir, "p3_model_data_from_phase_1_to_end_full.csv"))
data<-data[which(data$cue %in% c("reversal")),]
fields <- c("visit", "drug_str", "cue", "model_str", "drug", "ids", "ta", "sb")
df<- assign_var_types(data, fields)
df$model_str <- mapvalues(df$model_str,
                            from = c("PHnk5", "RW3", "RW3ph", "RW5ph"),
                            #to =c("PH-5", "RW-outcome-3", "RW-phase-3", "RW-both-5"))
                            to =c("Pearce-Hall model", "Outcome-sensitive model", "Phase-sensitive model", "Phase- and outcome-sensitive model"))
df3 = df %>%
  group_by( model_str, ids) %>%
  summarise_at("BIC", mean, na.rm = TRUE)

df3 <- df3 %>% tidyr::pivot_wider(id_cols=c("ids"), names_from=model_str, values_from = BIC)
df3$best_model <- apply(df3[,2:5], 1, which.min)
df3$best_model <- mapvalues(df3$best_model,
                            from = c(1, 2, 3, 4),
                            to =c("PH-5", "RW-outcome-3", "RW-phase-3", "RW-both-5"))

counts = df3 %>% dplyr::count(best_model)
counts$perc <- counts$n / sum(counts$n)
print(counts)

### exceedence probabilities
# calculate relative akaike weights see Wagenmakers and Farell 2004
mcdf <- exp(t(apply(df3[,2:5], 1, function(x){x-min(x)})) * (-1/2))
mcdf <- round(t(apply(mcdf, 1, function(x){x/sum(x)})),3)

bms0 <- VB_bms(as.matrix(mcdf)) #
names(bms0)
bms0<- as.data.frame(bms0)
bms0$models <- c("PH-5", "RW-outcome-3", "RW-phase-3", "RW-both-5")
bms0$models <- factor(bms0$models,levels = c("PH-5", "RW-outcome-3", "RW-phase-3", "RW-both-5"))

print(bms0$pxp)

g <- ggplot(data=bms0, aes(y=pxp, x=models)) +
  geom_bar(stat = "summary", fun.y = "mean") +
  theme_bw() +
  raincloud_theme + 
  labs(y= "Exceedence probability", x="")  
g
```

## 3b/ Analysis of learning rates

```{r}
data<-read.csv(here::here(data_dir, "RW_3_norm_model_params.csv"))
data<-data[which(data$cue %in% c(3)),]
df<- reshape2::melt(data, id.var = c("visit_str", "drug_str", "ids", "sb"), measure.vars = c('alpha_sh', 'alpha_nosh'), variable.name="outcome", value.name = "alpha")
df$visit <- mapvalues(df$visit_str,
                         from = c("v1","v2","v3"),
                         to = c(1,2,3))
df$visit_str <- mapvalues(df$visit_str,
                         from = c("v1","v2","v3"),
                         to = c("Baseline", "Drug", "Follow-up"))

df3 = df %>%
  group_by( visit_str, drug_str) %>%
  summarise_at("alpha", mean, na.rm = TRUE)
df3

df3 = df %>%
  group_by( visit_str, drug_str) %>%
  summarise_at("alpha", sd, na.rm = TRUE)
df3
```

```{r}
data<-read.csv(here::here(data_dir, "RW_3_norm_model_params.csv"))
data<-data[which(data$cue %in% c(3)),]
df<- reshape2::melt(data, id.var = c("visit_str", "drug_str", "ids", "sb"), measure.vars = c('alpha_sh', 'alpha_nosh'), variable.name="outcome", value.name = "alpha")
df$visit <- mapvalues(df$visit_str,
                         from = c("v1","v2","v3"),
                         to = c(1,2,3))
df$visit_str <- mapvalues(df$visit_str,
                         from = c("v1","v2","v3"),
                         to = c("Baseline", "Drug", "Follow-up"))

fields <- c("visit_str", "drug_str", "outcome", "ids", "sb")
df<- assign_var_types(df, fields)
df$alpha[df$alpha==0] <- 0.0001

pal <- get_colors("ond")

### statistics ### 
m <- lmer(alpha ~ drug_str*visit_str*outcome + (1|ids) + (1|sb) , data=df)
gm <- glmmTMB(alpha ~ drug_str*visit_str*outcome + (1|ids) + (1|sb) , data=df, family = beta_family(link="logit"))
car::Anova(gm)

summary(gm)
fixef(gm)

```

### 3b-1/ Drug*Visit 
```{r}
df$visit_str <- mapvalues(df$visit_str,
                            from = c("v1", "v2", "v3"),
                            to =c("Baseline", "Drug", "Follow-up"))
df$outcome <- mapvalues(df$outcome,
                            from = c("alpha_sh", "alpha_nosh"),
                            to =c("Shock", "No-shock"))


emgm<-summary(emmeans(gm, specs = pairwise ~ drug_str*visit_str, adjust=adjustment_method))
emgm$emmeans$emmean <- inv.logit(emgm$emmeans$emmean)
print(emgm$emmeans)
#joint_tests(gm, by = c("drug_str"))


gm2a_emm <- emmeans(gm, specs = ~ drug_str * visit_str)
lincombs <- contrast(gm2a_emm,
               list(v1_v2_los=c(1,0,-1,0,0,0), 
                    v1_v3_los=c(1,0,0,0,-1,0),
                    v2_v3_los=c(0,0,1,0,-1,0),
                    v1_v2_plac=c(0,1,0,-1,0,0), 
                    v1_v3_plac=c(0,1,0,0,0,-1),
                    v2_v3_plac=c(0,0,0,1,0,-1),
                    v1_drug=c(1,-1,0,0,0,0),
                    v2_drug=c(0,0,1,-1,0,0),
                    v3_drug=c(0,0,0,0,1,-1)
                    )) # second one not changed
emmeans::test(lincombs, adjust=adjustment_method)

# add to paper
### contrast of contrasts - is the decrease more significant in one than the other - yes!
gm2a_emm <- emmeans(gm, specs = ~ drug_str * visit_str)
lincombs <- contrast(gm2a_emm,
               list(v2_v1_drug=c(-1,0,1,0,0,0),
                    v3_v1_drug=c(-1,0,0,0,1,0),
                    v2_v1_plac=c(0,-1,0,1,0,0),
                    v3_v1_plac=c(0,-1,0,0,0,1)
                    ), adjust=adjustment_method) # second one not changed
concon <- contrast(lincombs, list(v2_v1_drug_plac=c(1,0,-1,0),
                        v3_v1_drug_plac=c(0,1,0,-1)), adjust=adjustment_method)
print(summary(concon))



g <- ggplot(data = df, aes(y = alpha, x = visit_str, fill = drug_str)) +
geom_point(aes(y = alpha, colour=drug_str), position =   position_jitterdodge(  jitter.width = .05,  dodge.width = 0.45), size = 1.3, alpha = 0.8, show.legend = FALSE) +
geom_boxplot(width = .4, outlier.shape = NA, alpha = 0.7,lwd=1.2, show.legend = FALSE) +
stat_summary(geom="line", fun="median", size=1.5, aes(group=drug_str, color=drug_str), alpha=0.5, show.legend = TRUE) +
stat_summary(geom="point", fun="median", size=3, aes(group=drug_str, color=drug_str), show.legend = FALSE) +
expand_limits(x = 3) +
scale_color_manual(values = c(pal[1], pal[3]), name = "Group", labels = c("losartan", "placebo")) +
scale_fill_manual(values = c(pal[1], pal[3]), name = "Group", labels = c("losartan", "placebo")) +  
ylim(0, 0.53) +
theme_bw() +
raincloud_theme +
labs(y= "Learning rate", x="Visit") 
g

ggsave(here::here(figures_dir, "Fig3", "Figure3_raw.pdf"), width = 6.2, height = 4, dpi = 120)


```

#### 3b-2 Learning rates by outcome
```{r}
g <- ggplot(data = df, aes(y = alpha, x = outcome, fill = outcome)) +
geom_point(aes(y = alpha, colour=outcome), position =   position_jitterdodge(  jitter.width = .15,  dodge.width = 0.25), size = 1, alpha = 0.8, show.legend = FALSE) +
geom_boxplot(width = .4, outlier.shape = NA, alpha = 0.7,lwd=1.2, show.legend = FALSE) +
expand_limits(x = 3) +
scale_color_manual(values = c("gray1", "gray59"), name = "Outcome", labels = c("Shock", "No-shock")) +
scale_fill_manual(values = c("gray1", "gray59"), name = "Outcome", labels = c("Shock", "No-shock")) +
ylim(0, 0.53) +
theme_bw() +
raincloud_theme +
labs(y= "Learning rate", x="") 
g
ggsave(here::here(figures_dir, "Fig3", "Figure3c_raw.pdf"), width = 3, height = 4, dpi = 120)

```

## 3c/ Parameter recovery
```{r}
models <- c("PH", "RW3", "RW5", "RWph3") 

#models <- c("PH") 
for (m in models) {
  df <- read.csv(here::here(data_dir, paste0("param_recovery_", m, ".csv")))
  cdf <- cor(df, use="pairwise.complete.obs")
  corrplot::corrplot(cdf, method='number')
}

```



# 4/ Conjunnction analyses
## 4a/ Linking alpha to behavioural ratings


### 4a-1/ Linking behavioural and learning rates results, also check for RTs and blood pressure 

```{r fi2, fix.width=10, fig.height=10}
### behavioural 
data<-read.csv(here::here(data_dir,  "full_beh_dataset_p3.csv"))
data<-data[which(data$Trial_Type %in% 3),]
data<-data[which(data$trno_swchp %in% c(seq(-3, -1), seq(5,15))),]
data<-data[which(data$rev_type_4plot_swchp %in% c("acq","ext")),]
data <- data %>% mutate(prepost = 
                    case_when(trno_swchp %in% seq(-3,-1) ~ "pre", 
                              trno_swchp %in% seq(5, 15) ~ "post"), na.rm = FALSE)
data<-data[which(data$prepost %in% c("pre","post")),]
fields <- c("visit", "rev_type_4plot_swchp", "drug", "outcome", "id", "prepost", "sb")
df<- assign_var_types(data, fields)
df = df %>%
  group_by(prepost, id, drug_str, visit_str, visit, rev_type_4plot_swchp, sb) %>%
  summarise_at("prob", mean, na.rm = TRUE)
df$prepost = factor(df$prepost, levels=c("pre", "post"))
df = df %>% spread(prepost, prob, fill = NA, convert = FALSE, drop = TRUE, sep = NULL)
df["prepost"] =  df["post"]-df["pre"]

dfv <- df[(df$visit==2 & df$rev_type_4plot_swchp %in% "acq"), c( "visit", "id", "sb", "drug_str")]
for (v in c(1,2,3)) {
  dfi <- df[df$visit==v, c("rev_type_4plot_swchp", "prepost", "visit", "id")]
  
  dfi$rev_type_4plot_swchp <- mapvalues(dfi$rev_type_4plot_swchp,
                            from = c("acq", "ext"),
                            to = c(paste0("prepost_acq_v", toString(v)), paste0("prepost_ext_v", toString(v))))
  dfi = dfi %>% tidyr::spread(rev_type_4plot_swchp, prepost, fill = NA, convert = FALSE, drop = TRUE, sep = NULL)

  dfv <- merge(dfv, dfi[,c("id", paste0("prepost_acq_v", toString(v)), paste0("prepost_ext_v", toString(v)))], by=c("id"), all.x=TRUE)
}




### learning rates
dflr<-read.csv(here::here(data_dir,   "data_across_mods.csv"))
dflr$id <- dflr$ids_mdata

v1<-dflr[dflr$visit %in% c(1),c( "alpha_sh", "alpha_nosh", "id")]
v1$alpha_sh_v1 <- v1$alpha_sh
v1$alpha_nosh_v1 <- v1$alpha_nosh
v1$alpha_diff_v1 <- v1$alpha_sh_v1 - v1$alpha_nosh_v1
v1$alpha_v1 <- (v1$alpha_sh_v1 + v1$alpha_nosh_v1)/2

v2<-dflr[dflr$visit %in% c(2),c( "alpha_sh", "alpha_nosh", "id")]
v2$alpha_sh_v2 <- v2$alpha_sh
v2$alpha_nosh_v2 <- v2$alpha_nosh
v2$alpha_diff_v2 <- v2$alpha_sh_v2 - v2$alpha_nosh_v2
v2$alpha_v2 <- (v2$alpha_sh_v2 + v2$alpha_nosh_v2)/2

v3<-dflr[dflr$visit %in% c(3),c( "alpha_sh", "alpha_nosh", "id")]
v3$alpha_sh_v3 <- v3$alpha_sh
v3$alpha_nosh_v3 <- v3$alpha_nosh
v3$alpha_diff_v3 <- v3$alpha_sh_v3 - v3$alpha_nosh_v3
v3$alpha_v3 <- (v3$alpha_sh_v3 + v3$alpha_nosh_v3)/2

dfl <- merge(v1, v2, by="id", all=TRUE)
dfl <- merge(dfl,v3, by="id", all=TRUE)

df <- merge(dfv, dfl)

# add blood pressure data 
df <- merge(df, phys_df[,c("id", "vas_T1_bpsys", "vas_T2_bpsys", "vas_T1_bpdia", "vas_T2_bpdia" )], by="id", all=TRUE)
df$bpsys_diff <- df$vas_T2_bpsys - df$vas_T1_bpsys
df$bpdia_diff <- df$vas_T2_bpdia - df$vas_T1_bpdia

df$prepost_v2 <- (df$prepost_acq_v2 + (-1)*df$prepost_ext_v2)/2
df$prepost_v3 <- (df$prepost_acq_v3 + (-1)*df$prepost_ext_v3)/2

df$prepost_acq <- (df$prepost_acq_v1 + df$prepost_acq_v2 + df$prepost_acq_v3)/3
df$prepost_ext <- (df$prepost_ext_v1 + df$prepost_ext_v2 + df$prepost_ext_v3)/3


vars <- c( "alpha_sh", "alpha_nosh", "prepost_acq", "prepost_ext")
for(i in colnames(df[,vars])){
      df[is.na(df[,i]), i] <- median(df[,i], na.rm = TRUE)
}

metadf2 <- df
```

### check for blood pressure ovarall
```{r}
m <- lm(data=metadf2, prepost_v2 ~ drug_str*bpsys_diff)
anova(m)

m <- lm(data=metadf2, prepost_v3 ~ drug_str*bpdia_diff)
anova(m) 

m <- lm(data=metadf2, alpha_v2 ~ drug_str*bpdia_diff)
anova(m)

m <- lm(data=metadf2, alpha_v3 ~ drug_str*bpsys_diff)
anova(m)



```
#### correlation of learning rates (model) and probability adjustment (behavioural data) overall

```{r}

cordf <- data.frame()
vars <- c("alpha_sh", "alpha_nosh", "prepost_acq", "prepost_ext")
corrplot(cor(df[,vars]), method = 'number')

rc <- rcorr(as.matrix(df[, vars]), type = c("pearson"))
print(rc$r)
print(round(rc$P,4))


for (al in c("alpha_sh", "alpha_nosh")) {
  for (p in c("prepost_acq", "prepost_ext")) {
    c <- cor.test(df[,al], df[,p], method="pearson")
    cordf<-rbind(cordf,data.frame(varname=paste0(p, "_", al), r=c$estimate, t=c$statistic, df=c$parameter, pval=c$p.value))
  }
}


cordf$pval.holm= round(p.adjust(cordf$pval, method = adjustment_method),3)
  

cordf




```


## 4b/ Linking dosage to alpha

```{r}
data<-read.csv(here::here(data_dir,  "data_across_mods_pupiltype_amplitude.csv"))
df<-data[which(data$visit_str %in% c("v2")),]

df$dosage <- 50/df$weight
df$dosage[df$drug_str %in% "placebo"] <-0  
df <- df[df$drug_str %in% "losartan", ]

v1<-data[data$visit_str %in% c("v1"), c("ids_mdata", "alpha_sh", "alpha_nosh")]
v1 <- v1 %>% dplyr::rename( alpha_sh_v1 = alpha_sh, alpha_nosh_v1 = alpha_nosh, ids = ids_mdata)
v1$alpha_v1 <- (v1$alpha_sh_v1 + v1$alpha_nosh_v1)/2
v2 <- df
v2 <- v2 %>% dplyr::rename( alpha_sh_v2 = alpha_sh, alpha_nosh_v2 = alpha_nosh, ids = ids_mdata)
v2$alpha_v2 <- (v2$alpha_sh_v2 + v2$alpha_nosh_v2)/2
tdf <- base::merge(v1, v2, by="ids")
tdf$alpha_sh_diff12 <- tdf$alpha_sh_v2 - tdf$alpha_sh_v1
tdf$alpha_nosh_diff12 <- tdf$alpha_nosh_v2 - tdf$alpha_nosh_v1
tdf$alpha_diff12 <- tdf$alpha_v2 - tdf$alpha_v1

cdf <- cor(tdf[!is.na(tdf$dosage),c("dosage", "alpha_v2",  "alpha_sh_diff12", "alpha_nosh_diff12", "alpha_diff12")])
corrplot::corrplot(cdf, method='number')


m <- lm(data = tdf, alpha_v2 ~ dosage)
anova(m)
print(cor.test(tdf$dosage, tdf$alpha_v2), method="spearman")
g <- ggplot(data=tdf, aes(x=dosage, y=alpha_v2)) +
  geom_point() + 
  labs(y= "dosage (mg/kg)", x="learning rate on visit 2")  + 
  geom_smooth(method='lm', formula= y~x)
g

```


### Response time

```{r}
data<-read.csv(here::here(data_dir,  "full_beh_dataset_p3.csv"))

data<-data[which(data$Trial_Type %in% 3),]
data<-data[which(data$trno %in% seq(1,15)),]
data<-data[which(data$rev_type_4plot_onlypost %in% c("acq","ext")),]
data <- data[data$RT>0 & data$RT <10,]
df = data %>%
  group_by(id, drug_str, visit_str, rev_type_4plot_swchp, sb) %>%
  summarise_at("RT", mean, na.rm = TRUE)


m <- glmer(data=data, RT ~ drug_str*visit_str+rev_type_4plot_swchp + (1 | id) + (1 | sb), family = Gamma(link = "log"))
car::Anova(m)

```